Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies

### 2019-07-17 paper/referee_reply2.txt

We thank the referee...

1. Re: Discussion in Section 3.2.2

Referee: "So to be clear, you have two sources of scatter in R_1/2 at fixed M* that sum in quadrature: 1) The scatter between M* and R_Mpeak, and 2) An additional 0.2 scatter that you impose by hand. Does this not increase the scatter in the M*-Reff relation to more than the level of Somerville et al 2017? I'm not sure what the scatter in R_Mpeak is at fixed M*, but the M*-Reff relation does not have more than 0.2 dex scatter."

Reply:

We have added a clarifying sentence to Section 6 to address this potential source of confusion.

2. Section 4.3

"If you have found models for the galaxy-halo connection other than the tidal stripping model which provide a poor fit to the observations, please mention them in the paper. Otherwise other people will waste their time investigating them."

3. Jackknife error bars

"Jackknife was one of the error estimation methods that I mentioned, but what about the scatter between different Monte Carlo realisations of the model. Presumably each realisation, with different M* and R_1/2 values for each subhalo, gives a single line on Figs 4-6, so that the entire model effectively produces a band even before jackknifing. How big is this scatter relative to that between different subregions for the same realisation? Or am I missing something and the line can only be calculated over many realisations? I don't think the role of the Monte Carlo realisations is explained completely clearly. Also, why not add the band to the green lines in Fig 6? It would be good to see explicitly that these are consistent with 0."

4. Section 6

"The Desmond 2016, 2017 papers I was referring to were MNRAS 464 (4) 4160 and MNRAS 472 (1) L35. These papers use galaxies' M-R-V scalings to constrain the R_1/2--Mvir,c relation at fixed M*, after applying AM. They find that at fixed M*, R_1/2 is weakly anticorrelated with Mvir or c. Thus I would suggest that the positive R_1/2--Mvir correlation at fixed M* implied by your model is in conflict with galaxies' internal dynamics, for example by leading to a positive correlation between the residuals of the Tully-Fisher and mass-size relations, which is not observed. Perhaps you could add this caveat."

5. The final comment in the referee's second review partains to a qualitative comment we made in our response to the initial report. This issue is germane to ongoing follow-up work on the relation between galaxy size and halo spin, but is mostly tangential to the scope of the present work.

### 2019-07-17 paper/galsize_paper.tex
Revised text and added reply to referee comment 1

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here. In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}. In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.

>>>>

Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation. By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies. Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here. In our approach, the level of scatter about the $\langle\rhalf\vert\mstar\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}. Both modeling choices are germane to ongoing follow-up work discussed in \S\ref{sec:future}, in which we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
